### 2016-01-18 paper.tex
Don't start sentence with math symbol per @nearyvs suggestion
Past tense
Add comma per @nearyvs

Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which
was obtained using the Welch--Satterthwaite formula
\begin{equation}
    \nu_X = \frac{\left(s_X^2 + \sum_{k=1}^M b_k^2 \right)^2} {s_X^4/\nu_{s_X} +
    \sum_{k=1}^M b_k^4/\nu_{b_k}},
\end{equation}
where $\nu_{s_X}$ is the number of degrees of freedom associated with $s_X$ and
$\nu_{b_k}$ is the number of degrees of freedom associated with $b_k$.
$\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
samples (or turbine revolutions). $\nu_{b_k}$ was estimated as
\begin{equation}
    \nu_{b_k} = \frac{1}{2} \left( \frac{\Delta b_k}{b_k} \right)^{-2},
\end{equation}
where the quantity in parentheses is the relative uncertainty of $b_k$, assumed
to be 0.25.

@@

For each tow speed, a relevant quasi-steady duration was selected by manually
inspecting a plot of the $C_P$ time series, and then truncated to include a
whole number of blade passages. Over this duration relevant statistics are
calculated.

@@

All data processing and plotting code, along with the reduced dataset are
available from \cite{Bachant2015-RM2-data}. Note that this code will
automatically download raw data as necessary so users can perform a full
reanalysis of the measurements presented here.

>>>>

Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which
was obtained using the Welch--Satterthwaite formula
\begin{equation}
    \nu_X = \frac{\left(s_X^2 + \sum_{k=1}^M b_k^2 \right)^2} {s_X^4/\nu_{s_X} +
    \sum_{k=1}^M b_k^4/\nu_{b_k}},
\end{equation}
where $\nu_{s_X}$ is the number of degrees of freedom associated with $s_X$ and
$\nu_{b_k}$ is the number of degrees of freedom associated with $b_k$.
$\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
samples (or turbine revolutions). The degrees of freedom parameter $\nu_{b_k}$
was estimated as
\begin{equation}
    \nu_{b_k} = \frac{1}{2} \left( \frac{\Delta b_k}{b_k} \right)^{-2},
\end{equation}
where the quantity in parentheses is the relative uncertainty of $b_k$, assumed
to be 0.25.

@@

For each tow speed, a relevant quasi-steady duration was selected by manually
inspecting a plot of the $C_P$ time series, and then truncated to include a
whole number of blade passages. Over this duration relevant statistics were
calculated.

@@

All data processing and plotting code, along with the reduced dataset, are
available from \cite{Bachant2015-RM2-data}. Note that this code will
automatically download raw data as necessary so users can perform a full
reanalysis of the measurements presented here.
